Synthesizing Quotient Lenses

### 2018-02-25 papers/QuotientLenses/main.tex
Added abstract

\begin{document}
\title{Synthesizing Quotient Lenses}
\begin{abstract}
\saz{The old abstract read more like an introduction, so we modified it to be
the ``new'' introduction.}
\end{abstract}

\keywords{quotient lenses, synthesis}
\maketitle              % typeset the title of the contribution

@@

The following list summarizes the central contributions of our work.
\begin{enumerate}
  \item We introduce {\em Quotient Regular Expressions} (QREs),
  a compact, convenient notation for defining (1) a
  regular language modulo some equivalence relation, and (2) a canonizer
  for that relation (Section~\ref{QRE}).
  \item We define a language of {\em QRE lenses}.  This language is
  a subset of the full set of bijective quotient
  lenses whose types are given by QREs. Our main technical contribution
  is a proof that our QREs are just as expressive as the full set of bijective
  quotient lenses.
  % In other words, if there eeach QRE lens $q$ defines the same transformation as a
  %QRE lens $q'$ that is in normal form.
  (Section~\ref{QRE-lenses}).
  \item We reduce the problem of {\em synthesizing}
  QRE lenses to the previously studied problem of synthesizing bijective lenses
  between regular languages (Section~\ref{synth}).
  \item We extend the Boomerang {\em implementation} with QREs
  and QRE lens synthesis.  We demonstrate the utility of our
  implementation by using it to
  synthesize QRE lenses between data formats drawn from the
  {\tt data.gov} database (Section~\ref{impl}).
\end{enumerate}
Sections~\ref{relwork} and~\ref{concl} discuss related and future work.

@@

\subsection{Quotient Regular Expressions}

@@

This section introduces Quotient Regular Expressions or QREs. QREs are regular
expressions augmented with syntax that lets them simultaneously express a
language and how to convert from that language into its canonical elements.

\subsection{Syntax of Quotient Regular Expressions}
The language of Quotient Regular Expressions (QREs) is given by the following
grammar:
\begin{align*}
c := \; &R \sep \project{R}{s} \sep \squash{c}{c'}{f} \sep
\perm{c_1, \ldots, c_n}{c} \\
& | \; \normalize{R}{R'}{f} \sep c \semicolon c' \sep c \cdot c''' \sep (c \sep
c') \sep c^*,
\end{align*}
where $c$ ranges over QREs, $R$ ranges over regular expressions, $f$ ranges over
functions between regular languages, and $s$ ranges over character strings. In
the following sections, we will use the the notation $\mathcal{L}(R)$ to mean
the language accepted by the regular expression $R$.

>>>>

\begin{document}
\title{Synthesizing Quotient Lenses}
\begin{abstract}
While there currently exist many bidirectional programming languages, many of
them do not have built-in support for transformations that operate on data
modulo equivalence relations such as whitespace or permutation quotienting.
Moreover, langauges such as Boomerang which do allow for such transformations
are often difficult to program \sam{why?}. To address these shortcomings, this
paper (1) introduces a language of {\em quotient regular expressions} or QREs
for defining equivalences on regular expressions as well as a language of {\em
QRE lenses}, which are lenses that map between QREs, and (2) shows how to {\em
synthesize} QRE lenses from a pair of QREs and a set of example input-output
pairs. We also describe an implementation of QREs and QRE lens synthesis in
Boomerang, and demonstrate the utility of our implementation by using it to
synthesize QRE lenses between data formats drawn from {\tt data.gov} database.
\end{abstract}

\keywords{quotient regular expressions, QRE lens, synthesis}
\maketitle

@@

The following list summarizes the central contributions of our work.
\begin{enumerate}
  \item We introduce {\em Quotient Regular Expressions} (QREs),
  a compact, convenient notation for defining (1) a
  regular language modulo some equivalence relation, and (2) a canonizer
  for that relation (Section~\ref{QRE}).
  \item We define a language of {\em QRE lenses}.  This language is
  a subset of the full set of bijective quotient
  lenses whose types are given by QREs. Our main technical contribution
  is a proof that our QREs are just as expressive as the full set of bijective
  quotient lenses.
  % In other words, if there eeach QRE lens $q$ defines the same transformation as a
  %QRE lens $q'$ that is in normal form.
  (Section~\ref{QRE-lenses}).
  \item We reduce the problem of {\em synthesizing}
  QRE lenses to the previously studied problem of synthesizing bijective lenses
  between regular languages (Section~\ref{synth}).
  \item We extend the Boomerang {\em implementation} with QREs
  and QRE lens synthesis.  We demonstrate the utility of our
  implementation by using it to
  synthesize QRE lenses between data formats drawn from the
  {\tt data.gov} database (Section~\ref{impl}).
\end{enumerate}
Sections~\ref{relwork} discusses related work and~\ref{concl} summarizes the
results of the paper.

@@

\subsection{Quotient Regular Expressions}
\label{subsec:qre-expressions}

@@

Quotient Regular Expressions allow programs to specify a regular language,
an equivalence relation over elements of the language and a function to convert
elements of the language into normal form.

\subsection{Syntax}

The language of Quotient Regular Expressions (QREs) is given by the following
grammar:
\begin{align*}
c := \; &R \sep \project{R}{s} \sep \squash{c}{c'}{f} \sep
\perm{c_1, \ldots, c_n}{c} \\
& | \; \normalize{R}{R'}{f} \sep c \semicolon c' \sep c \cdot c''' \sep (c \sep
c') \sep c^*,
\end{align*}
where $c$ ranges over QREs, $R$ ranges over regular expressions, $f$ ranges over
functions between regular languages, and $s$ ranges over character strings.
$\mathcal{L}(R)$ is
the language accepted by the regular expression $R$.

%Section~\ref{subsec:qre-expressions} presented a number of examples
